### 2016-02-10 Plos-one-manuscript/latex/manuscript.tex
working on manuscript

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[]
\centering
\caption{
\bf{Comparison of error between the printed and commercially produced pipette}}
\begin{tabular}{llllll}
                  Volume &   & Systematic error &  & Random error & \\
                  \hline
\multirow{2}{*}{10 $\mu$L} & printed & 2.17 \% & $\pm$0.217$\mu$L  & 1.96\% & $\pm$0.196$\mu$L   \\
                  & commercial & 3\% & $\pm$0.3$\mu$L  & 1\% & $\pm$0.1$\mu$L  \\
                  \hline
\multirow{2}{*}{20 $\mu$L} & printed  & 0.33\% & $\pm$0.066$\mu$L & 1.18 \% & $\pm$0.236$\mu$L \\
                  & commercial & 2.50\% & $\pm$0.5$\mu$L & 0.70\% & $\pm$0.14$\mu$L \\
                  \hline
\multirow{2}{*}{50 $\mu$L} & printed & 1.17\% & $\pm$0.585$\mu$L & 0.50\% & $\pm$0.25$\mu$L \\
                  & commercial & 1\% & $\pm$0.5$\mu$L & 0.30\% & $\pm$0.15$\mu$L \\
                  \hline
\multirow{2}{*}{200 $\mu$L} & printed & 2.52\% & $\pm$5.04$\mu$L & 0.69\% & $\pm$1.38$\mu$L  \\
                  & commercial & 0.6\% & $\pm$1.2$\mu$L & 0.20\% & $\pm$0.4$\mu$L
\end{tabular}
\begin{flushleft} Error assessed for average measured volume by weight of water compared with published specifications of commercial pipette. [Alos compare to data taken with commercial pipettes in our lab]
\end{flushleft}
\label{table1}
\end{table}

>>>>

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[]
\centering
\caption{
\bf{Comparison of error between the printed and commercially produced pipette}}
\begin{tabular}{llllll}
                  Volume &   & Systematic error &  & Random error & \\
                  \hline
\multirow{2}{*}{10 $\mu$L} & printed & 2.17 \% & $\pm$0.217$\mu$L  & 1.96\% & $\pm$0.196$\mu$L   \\
                  & commercial & 3\% & $\pm$0.3$\mu$L  & 1\% & $\pm$0.1$\mu$L  \\
                  \hline
\multirow{2}{*}{20 $\mu$L} & printed  & 0.33\% & $\pm$0.066$\mu$L & 1.18 \% & $\pm$0.236$\mu$L \\
                  & commercial & 2.50\% & $\pm$0.5$\mu$L & 0.70\% & $\pm$0.14$\mu$L \\
                  \hline
\multirow{2}{*}{50 $\mu$L} & printed & 1.17\% & $\pm$0.585$\mu$L & 0.50\% & $\pm$0.25$\mu$L \\
                  & commercial & 1\% & $\pm$0.5$\mu$L & 0.30\% & $\pm$0.15$\mu$L \\
                  \hline
\multirow{2}{*}{200 $\mu$L} & printed & 2.52\% & $\pm$5.04$\mu$L & 0.69\% & $\pm$1.38$\mu$L  \\
                  & commercial & 0.6\% & $\pm$1.2$\mu$L & 0.20\% & $\pm$0.4$\mu$L
\end{tabular}
\begin{flushleft} Error assessed for average measured volume by weight of water compared with published specifications of commercial pipette. [Alos compare to data taken with commercial pipettes in our lab]
\end{flushleft}
\label{table0}
\end{table}

\begin{table}[]
\centering
\caption{\bfseries{Commercial and Printed pipettes compared to ISO standard 8655.}}
\label{my-label}
\begin{tabular}{lllllll}
Volume & Pipette & Mean   & SE    & \% SE & RE & \% RE \\
       & ISO, 20-200 $\mu$L & 200 $\mu$L       & $\pm$1.60         & $\pm$0.08          & 0.60 & 0.30 \\
200 $\mu$L & Commercial & 198.23       & -1.77        & -0.88         & 1.14 & 0.58 \\
       & Printed  & 193.40       & -6.60        & -3.30         & 2.86 & 1.48 \\
       &                     &              &              &               &      &      \\
       & ISO, 20-200 $\mu$L & 50 $\mu$L        & $\pm$1.60         &$\pm$3.20          & 0.60 & 1.20 \\
50 $\mu$L  & Commercial   & 48.89        & -1.11        & -2.23         & 0.71 & 1.46 \\
       & Printed      & 49.62        & -0.38        & -0.76         & 1.26 & 2.53 \\
       &                     &              &              &               &      &      \\
       & ISO, 20-200 $\mu$L & 20 $\mu$L        & $\pm$1.60         & $\pm$8.00          & 0.60 & 3.00 \\
20 $\mu$L  & Commercial   & 20.16        & 0.16         & 0.81          & 0.16 & 0.81 \\
       & Printed     & 18.70        & -1.30        & -6.48         & 0.38 & 2.01 \\
       &                     &              &              &               &      &      \\
       & ISO, 10-100 $\mu$L & 10 $\mu$L        & $\pm$0.80         & $\pm$8.00          & 0.30 & 3.00 \\
10 $\mu$L  & Commercial   & 9.88         & -0.12        & -1.23         & 0.34 & 3.39 \\
       & Printed      & 11.95        & 1.95         & 19.52         & 0.73 & 6.08 \\
       &                     &              &              &               &      &      \\
       & ISO, 20-200 $\mu$L & 10 $\mu$L        & $\pm$1.60         & $\pm$16.00         & 0.60 & 6.00 \\
10 $\mu$L* & Commercial   & 9.88         & -0.12        & -1.23         & 0.34 & 3.39 \\
       & Printed      & 11.95        & 1.95         & 19.52         & 0.73 & 6.08
\end{tabular}
\begin{flushleft} Commercial and Printed pipettes compared to ISO standard 8655.
\end{flushleft}
\label{table1}
\end{table}
